### 2024-01-26 ms.qmd
Updates

#### Learning  
To estimate learning skills, we tested skinks' ability to locate a food reward in a series of behavioural tasks (@fig-Methods B) [see @leal_behavioural_2012; @clark_colour_2014]. First, we performed a training phase where lizards had to learn to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm) identical to the ones from the experiment except for the colour (see below). We divided this training phase into three stages: in the first stage, lizards had to eat a small, frozen cricket (*A. domestica*) from an opaque petri dish (3D x 1.6H cm) placed in the middle of their enclosure (@fig-Methods B, Stage 1); in the second stage, the petri dish with the cricket was placed on top of the white 3D printed ramps (@fig-Methods B, Stage 2); and finally, the cricket was left inside a well (3D x 1.75H cm) on the top of the ramp in the third and last stage (Fig. @fig-Methods B, Stage 3). Every trial began when we left the feeding block (petri dish, ramp, or both) inside the enclosure and finished one hour later when we took it away. At the end of each trial, we recorded whether the cricket had been consumed or not. Trial was considered successful if the lizard could locate and consume the reward, while completion of each stage required the lizards to eat the crickets in at least 5 out of 6 trials. This phase lasted 38 days until all the lizards were able to eat from the ramp; only in one case we decided not to use the lizard because its behaviour was not consistent over the course of the training phase.  
For the learning phase, we trained lizards to associate between colour and a food reward (Associative task in Fig. @fig-Methods B). The test was like the third stage of the training phase, but here lizards were presented with three feeders that differed in the colour. We placed the food reward (small, frozen, *A. domestica* crickets) inside the wells of the three feeders, covering two of the crickets with 3D-printed lids (3D x 0.5H cm) so prey was only accessible in "the correct" ramp. The food reward was placed in all three wells to avoid lizard using prey chemical cues, and the lids had a series of small holes on the top to allow the release of those chemicals. The colours of the feeders were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision]. To control for potential colour preference that could bias our results (see Supplementary Material), we split the subjects into two groups counterbalanced by treatment and species: in one group the correct choice (i.e., the ramp with the non-covered frozen cricket) was the blue one during the associative task and red in the reversal, while for the other group we assigned red as correct for the associative and blue for the reversal. In all trials, the position of the feeders was changed randomly to ensure subjects were using colour rather than spatial cues for the association. Lizards were tested in this task once a day for 35 days.  
The full experiment was done daily between the 6^th^ of March until the 17^th^ of June 2023, between 11 to 12 am, when the lizards were active. Trials in the learning phases (colour associative task and reversal tasks) were recorded with CCTV systems always using the same camera per individual. Videos were analysed manually using a standard video player (IINA) by PR, who recorded whether the first choice made by each subject was the correct feeder or not. A choice was considered to be made if the head of the lizard was inside the well of one of the ramps. PR was blinded to the treatments of the lizards during the analyses of the video. We considered a trial failed if there was no choice in one hour of recording and those trials were considered as 'non data' in the analyses. We excluded from our analyses those individuals with more than 15 trials failed (i.e. they did not make a choice), and we considered the first trial to be the first one where the individual made a choice.

@@

#### Statistical analyses  
We performed the analyses with species (_L. delicata_ or _L. guichenoti_) separately. We also saw a significant effect of the colour assigned in the preliminary analises, so we decided to split the data by colour ('Blue' or 'Red') as well. As such, we run a total of four different Bayesian multilevel models using the brm function from the brms package (@burkner2017brms) in Quarto (@Allaire_Quarto_2022). Each model consisted of four parallel chains of 3000 iterations, with a warm up interval of 1000 iterations.'Choice', i.e. whether the feeder visited first was the correct one (1) or not (0) was used as the response variable. The fixed effects of the model included a triple interaction between: 'Trial' as a nummeric variable, and hormone treatmet ('CORT' versus 'Control') and the temperature at which eggs were incubated ('Cold' versus 'Hot') as factors. For the random effects, we employed lizard identity as a random intercept, and as a random slope we included the 'Trial' within each level of lizard identity.  
We used the resulting posterior of these models to evaluate learning differences between treatments within and between species and colour assigned. More specifically, we calculated learning slopes by using the estimates of the trial variable per each level of the hormone-temperature interaction ('Treatments'); values bigger from zero were considered as evidence of learning, while those less or equal to zero not. We used the pmcmc method to test whether those slopes or the comparissons between 'Treatments' (e.g. slope for 'CORT-Cold' lizards minus 'CORT-Hot' lizards) were different from zero (two-tailed tests). We considered statistical significance if p-value < 0.05.

@@

Originally, we started with 96 lizards, 48 per species and 12 per treatment per species. However, due to natural mortality (n = 11), no completion of the training stage (n = 1), or no motivation during the learning tasks (n = 3; see above), we ended up with a total of 81 lizards. Final sample sizes per treatment and species are disclosed on @tbl-data.  
```{r, models}
#| label: models
# Fitting the model and extraction of posteriors for both species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
source(here("R", "func.R"))
# Model formula: FC_associative ~ Trial*cort*temp + (1 + Trial|lizard_id)
## A.1) L. delicata
deli_red <- fit_m("deli", "red", refit = TRUE)
write.csv(deli_red, file= "./output/Checking/deli_red.csv")
deli_blue <- fit_m("deli", "blue", refit = TRUE)
write.csv(deli_blue, file= "./output/Checking/deli_blue.csv")
## A.2) L. guichenoti
guich_red <- fit_m("guich", "red", refit = TRUE)
write.csv(guich_red, file= "./output/Checking/guich_red.csv")
guich_blue <- fit_m("guich", "blue", refit = TRUE)
write.csv(guich_blue, file= "./output/Checking/guich_blue.csv")
```

@@

Results of the are summarized in @tbl-data and figures @Figdeli, @Figguich. On average, we found that the estimated learning slopes were lower when the blue feeders were the correct choice compared to those assigned to the group 'Red'  for _L. delicata_ ('Blue' learning slope - 'Red'learning slope = `r format_dec(mean((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (dar_CORTCold + dar_ControlCold + dar_CORTCold + dar_ControlHot)), 3)`, p = `r format_dec(pmcmc((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (dar_CORTCold + dar_ControlCold + dar_CORTCold + dar_ControlHot)), 3)`), but not for _L. guichenoti_ ('Blue' learning slope - 'Red'learning slope = `r format_dec(mean((gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTCold + gar_ControlHot)), 3)`, p = `r format_dec(pmcmc((gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTCold + gar_ControlHot)),3)`). However, further analyses using the first trial indicated a potential bias towards 'Blue' in the initial choice (see Supplementary Material and Figs. @Figdeli, @Figguich); and in consequence, we only used those individuals assigned to 'Red' to compare between-treatment performance. In this regard, we did not find any significant differences between treatments for _L. delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(dar_ControlCold - dar_CORTCold), 3)`, p- value = `r format_dec(pmcmc(dar_ControlCold - dar_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(dar_ControlHot- dar_CORTHot), 3)`, p- value = `r format_dec(pmcmc(dar_ControlHot - dar_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(dar_ControlHot - dar_ControlCold), 3)`, p-value = `r format_dec(pmcmc(dar_ControlHot - dar_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(dar_CORTHot - dar_CORTCold), 3)`, p-value = `r format_dec(pmcmc(dar_CORTHot - dar_CORTCold), 3)`) (see @Figdeli), or _L. guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(gar_ControlCold - gar_CORTCold), 3)`, p- value = `r format_dec(pmcmc(gar_ControlCold - gar_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(gar_ControlHot- gar_CORTHot), 3)`, p- value = `r format_dec(pmcmc(gar_ControlHot - gar_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(gar_ControlHot - gar_ControlCold), 3)`, p-value = `r format_dec(pmcmc(gar_ControlHot - gar_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(gar_CORTHot - gar_CORTCold), 3)`, p-value = `r format_dec(pmcmc(gar_CORTHot - gar_CORTCold), 3)`) (see @Figguich). When groups were pooled by incubation temperature or hormonal treatment, there was not significant differences in the estimated slopes caused by temperature (_L. delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((dar_CORTHot + dar_ControlHot) - (dar_CORTCold + dar_ControlCold)),3)`, p-value = `r format_dec(pmcmc((dar_CORTHot + dar_ControlHot) - (dar_CORTCold + dar_ControlCold)),3)`; _L. guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((gar_CORTHot + gar_ControlHot)-(gar_CORTCold + gar_ControlCold)),3)`, p-value = `r format_dec(pmcmc((gar_CORTHot + gar_ControlHot)-(gar_CORTCold + gar_ControlCold)),3)`) or the hormone (_L. delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((dar_ControlCold + dar_ControlHot) - (dar_CORTCold + dar_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((dar_ControlCold + dar_ControlHot) - (dar_CORTCold + dar_CORTHot)), 3)` ; _L. guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((gar_ControlCold + gar_ControlHot)-(gar_CORTCold + gar_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((gar_ControlCold + gar_ControlHot)-(gar_CORTCold + gar_CORTHot)), 3)`). We also did not find any significant differences when we compared the estimated slopes between species (_L. delicata_ - _L. guichenoti_ = `r format_dec(mean((dar_CORTCold + dar_ControlCold + dar_CORTHot + dar_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTHot + gar_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((dar_CORTCold + dar_ControlCold + dar_CORTHot + dar_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTHot + gar_ControlHot)), 3)`).

```{r, figdeli}
#| label: figdeli
#| fig.cap: "Deli"
# First step, create the Intercepts for all models
## 1) Associative task
### Group = red
int_dar_CORTCold <- deli_red$b_Intercept
int_dar_ControlCold <- (deli_red$b_cortControl + deli_red$b_Intercept)
int_dar_CORTHot <- (deli_red$b_tempHot + deli_red$b_Intercept)
int_dar_ControlHot <- (deli_red$'b_cortControl:tempHot' + deli_red$b_cortControl + deli_red$b_tempHot + deli_red$b_Intercept)
### Group = blue
int_dab_CORTCold <- deli_blue$b_Intercept
int_dab_ControlCold <- (deli_blue$b_cortControl + deli_blue$b_Intercept)
int_dab_CORTHot <- (deli_blue$b_tempHot + deli_blue$b_Intercept)
int_dab_ControlHot <- (deli_blue$'b_cortControl:tempHot' + deli_blue$b_cortControl + deli_blue$b_tempHot + deli_blue$b_Intercept)
## 2) Reversal task
### Group = red
int_drr_CORTCold <- deli_rev_red$b_Intercept
int_drr_ControlCold <- (deli_rev_red$b_cortControl + deli_rev_red$b_Intercept)
int_drr_CORTHot <- (deli_rev_red$b_tempHot + deli_rev_red$b_Intercept)
int_drr_ControlHot <- (deli_rev_red$'b_cortControl:tempHot' + deli_rev_red$b_cortControl + deli_rev_red$b_tempHot + deli_rev_red$b_Intercept)
### Group = blue
int_drb_CORTCold <- deli_rev_blue$b_Intercept
int_drb_ControlCold <- (deli_rev_blue$b_cortControl + deli_rev_blue$b_Intercept)
int_drb_CORTHot <- (deli_rev_blue$b_tempHot + deli_rev_blue$b_Intercept)
int_drb_ControlHot <- (deli_rev_blue$'b_cortControl:tempHot' + deli_rev_blue$b_cortControl + deli_rev_blue$b_tempHot + deli_rev_blue$b_Intercept)
# Second step, create the df for each model with trials as columns and the predicted probability of choosing right as rows under equation: Prob = 1/(1+e^-(Intercept + Slope*trial))??
## 1) Associative task
### Group = red
#### CORT-Cold

>>>>

#### Learning  
To estimate learning skills, we tested skinks' ability to locate a food reward in a series of behavioural tasks (@fig-Methods B) [see @leal_behavioural_2012; @clark_colour_2014]. First, we performed a training phase where lizards had to learn to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm) identical to the ones from the experiment except for the colour (see below). We divided this training phase into three stages: in the first stage, lizards had to eat a small, frozen cricket (*A. domestica*) from an opaque petri dish (3D x 1.6H cm) placed in the middle of their enclosure (@fig-Methods B, Stage 1); in the second stage, the petri dish with the cricket was placed on top of the white 3D printed ramps (@fig-Methods B, Stage 2); and finally, the cricket was left inside a well (3D x 1.75H cm) on the top of the ramp in the third and last stage (Fig. @fig-Methods B, Stage 3). Every trial began when we left the feeding block (petri dish, ramp, or both) inside the enclosure and finished one hour later when we took it away. At the end of each trial, we recorded whether the cricket had been consumed or not. Trial was considered successful if the lizard could locate and consume the reward, while completion of each stage required the lizards to eat the crickets in at least 5 out of 6 trials. This phase lasted 38 days until all the lizards were able to eat from the ramp; only in one case we decided not to use the lizard because its behaviour was not consistent over the course of the training phase.  
For the learning phase, we trained lizards to associate between colour and a food reward ('Associative task' in Fig. @fig-Methods B). The test was like the third stage of the training phase, but here lizards were presented with three feeders that differed in the colour. We placed the food reward (small, frozen, *A. domestica* crickets) inside the wells of the three feeders, covering two of the crickets with 3D-printed lids (3D x 0.5H cm) so prey was only accessible in "the correct" ramp. The food reward was placed in all three wells to avoid lizard using prey chemical cues, and the lids had a series of small holes on the top to allow the release of those chemicals. The colours of the feeders were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision]. To control for potential colour preference that could bias our results we split the subjects into two groups counterbalanced by treatment and species: in one group the correct choice (i.e., the ramp with the non-covered frozen cricket) was the blue one, while for the other group we assigned red as correct. In all trials, the position of the feeders was changed randomly to ensure subjects were using colour rather than spatial cues for the association. Lizards were tested in this task once a day for 35 days.  
The full experiment was done daily between the 6^th^ of March until the 17^th^ of June 2023, between 11 to 12 am, when the lizards were active. Trials in the learning phase were recorded with CCTV systems always using the same camera per individual. Videos were analysed manually using a standard video player (IINA) by PR, who recorded whether the first choice made by each subject was the correct feeder or not. A choice was considered to be made if the head of the lizard was inside the well of one of the ramps. PR was blinded to the treatments of the lizards during the analyses of the video. We considered a trial failed if there was no choice in one hour of recording and those trials were considered as 'non data' in the analyses. We excluded from our analyses those individuals with more than 15 trials failed (i.e. they did not make a choice), and we considered the first trial to be the first one where the individual made a choice.

@@

#### Statistical analyses  
We performed the analyses with species (_L. delicata_ or _L. guichenoti_) separately. We also saw a significant effect of the colour assigned in the preliminary analises, so we decided to split the data by colour (blue or red) as well. As such, we run a total of four different Bayesian multilevel models using the brm function from the brms package (@burkner2017brms) in Quarto (@Allaire_Quarto_2022). Each model consisted of four parallel chains of 3000 iterations, with a warm up interval of 1000 iterations. 'Choice', i.e. whether the feeder visited first was the correct one (1) or not (0) was used as the response variable. The fixed effects of the model included a triple interaction between: 'Trial' as a nummeric variable, and hormone treatmet ('CORT' versus 'Control') and the temperature at which eggs were incubated ('Cold' versus 'Hot') as factors. For the random effects, we employed lizard identity as a random intercept, and as a random slope we included the 'Trial' within each level of lizard identity.  
We used the resulting posterior of these models to evaluate learning differences between treatments within and between species and colour assigned. More specifically, we calculated learning slopes by using the estimates of the trial variable per each level of the hormone-temperature interaction ('Treatments'); values bigger from zero were considered as evidence of learning, while those less or equal to zero not. We used the pmcmc method to test whether those slopes or the comparissons between treatments (e.g. slope for 'CORT-Cold' lizards minus 'CORT-Hot' lizards) were different from zero (two-tailed tests). We considered statistical significance if p-value < 0.05.

@@

Originally, we started with 96 lizards, 48 per species and 12 per treatment per species. However, due to natural mortality (n = 11), no completion of the training stage (n = 1), or no motivation during the learning tasks (n = 3), we ended up with a total of 81 lizards. Final sample sizes per treatment and species are disclosed on @tbl-data.  
```{r, models}
#| label: models
# Fitting the model and extraction of posteriors for both species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
source(here("R", "func.R"))
# Model formula: FC_associative ~ Trial*cort*temp + (1 + Trial|lizard_id)
## A.1) L. delicata
deli_red <- fit_m("deli", "red", refit = FALSE)
write.csv(deli_red, file= "./output/Checking/deli_red.csv")
deli_blue <- fit_m("deli", "blue", refit = FALSE)
write.csv(deli_blue, file= "./output/Checking/deli_blue.csv")
## A.2) L. guichenoti
guich_red <- fit_m("guich", "red", refit = FALSE)
write.csv(guich_red, file= "./output/Checking/guich_red.csv")
guich_blue <- fit_m("guich", "blue", refit = FALSE)
write.csv(guich_blue, file= "./output/Checking/guich_blue.csv")
```

@@

Results of the are summarized in @tbl-data and figures @Figdeli, @Figguich. On average, we found that the estimated learning slopes were lower when the blue feeders were the correct choice compared to those assigned to the group 'Red' for _L. delicata_ ('Blue' learning slope - 'Red'learning slope = `r format_dec(mean((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (dar_CORTCold + dar_ControlCold + dar_CORTCold + dar_ControlHot)), 3)`, p = `r format_dec(pmcmc((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (dar_CORTCold + dar_ControlCold + dar_CORTCold + dar_ControlHot)), 3)`), but not for _L. guichenoti_ ('Blue' learning slope - 'Red'learning slope = `r format_dec(mean((gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTCold + gar_ControlHot)), 3)`, p = `r format_dec(pmcmc((gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTCold + gar_ControlHot)),3)`). However, further analyses using the first trial indicated a potential bias towards blue in the initial choice (see Supplementary Material and Figs. @Figdeli, @Figguich) that could be affecting the estimated slopes. As such, we analysed the between treatments differences for each group separately.  
For those individuals assigned to group 'Red', we did not find any significant differences between treatments neither for _L. delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(dar_ControlCold - dar_CORTCold), 3)`, p- value = `r format_dec(pmcmc(dar_ControlCold - dar_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(dar_ControlHot- dar_CORTHot), 3)`, p- value = `r format_dec(pmcmc(dar_ControlHot - dar_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(dar_ControlHot - dar_ControlCold), 3)`, p-value = `r format_dec(pmcmc(dar_ControlHot - dar_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(dar_CORTHot - dar_CORTCold), 3)`, p-value = `r format_dec(pmcmc(dar_CORTHot - dar_CORTCold), 3)`) (see @Figdeli), or _L. guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(gar_ControlCold - gar_CORTCold), 3)`, p- value = `r format_dec(pmcmc(gar_ControlCold - gar_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(gar_ControlHot- gar_CORTHot), 3)`, p- value = `r format_dec(pmcmc(gar_ControlHot - gar_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(gar_ControlHot - gar_ControlCold), 3)`, p-value = `r format_dec(pmcmc(gar_ControlHot - gar_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(gar_CORTHot - gar_CORTCold), 3)`, p-value = `r format_dec(pmcmc(gar_CORTHot - gar_CORTCold), 3)`) (see @Figguich). However, in both species the slope in the 'CORTCold' treatments seems bigger than the rest for group 'Red'. When groups were pooled by incubation temperature, slopes from individuals incubated at 23ºC were on average bigger in both species, but the difference was not significant (_L. delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((dar_CORTHot + dar_ControlHot) - (dar_CORTCold + dar_ControlCold)),3)`, p-value = `r format_dec(pmcmc((dar_CORTHot + dar_ControlHot) - (dar_CORTCold + dar_ControlCold)),3)`; _L. guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((gar_CORTHot + gar_ControlHot)-(gar_CORTCold + gar_ControlCold)),3)`, p-value = `r format_dec(pmcmc((gar_CORTHot + gar_ControlHot)-(gar_CORTCold + gar_ControlCold)),3)`). CORT also lead to higher slopes in both species, but the differences were not significant (_L. delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((dar_ControlCold + dar_ControlHot) - (dar_CORTCold + dar_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((dar_ControlCold + dar_ControlHot) - (dar_CORTCold + dar_CORTHot)), 3)` ; _L. guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((gar_ControlCold + gar_ControlHot)-(gar_CORTCold + gar_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((gar_ControlCold + gar_ControlHot)-(gar_CORTCold + gar_CORTHot)), 3)`). We also did not find any significant differences when we compared the estimated slopes between species (_L. delicata_ - _L. guichenoti_ = `r format_dec(mean((dar_CORTCold + dar_ControlCold + dar_CORTHot + dar_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTHot + gar_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((dar_CORTCold + dar_ControlCold + dar_CORTHot + dar_ControlHot) - (gar_CORTCold + gar_ControlCold + gar_CORTHot + gar_ControlHot)), 3)`).  
The results for 'Blue' individuals were similar. We did not find significant differences between treatments in _L.delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(dab_ControlCold - dab_CORTCold), 3)`, p- value = `r format_dec(pmcmc(dab_ControlCold - dab_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(dab_ControlHot- dab_CORTHot), 3)`, p- value = `r format_dec(pmcmc(dab_ControlHot - dab_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(dab_ControlHot - dab_ControlCold), 3)`, p-value = `r format_dec(pmcmc(dab_ControlHot - dab_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(dab_CORTHot - dab_CORTCold), 3)`, p-value = `r format_dec(pmcmc(dab_CORTHot - dab_CORTCold), 3)`) (see @Figdeli), or _L. guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(gab_ControlCold - gab_CORTCold), 3)`, p- value = `r format_dec(pmcmc(gab_ControlCold - gab_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(gab_ControlHot- gab_CORTHot), 3)`, p- value = `r format_dec(pmcmc(gab_ControlHot - gab_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(gab_ControlHot - gab_ControlCold), 3)`, p-value = `r format_dec(pmcmc(gab_ControlHot - gab_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(gab_CORTHot - gab_CORTCold), 3)`, p-value = `r format_dec(pmcmc(gab_CORTHot - gab_CORTCold), 3)`) (see @Figguich). However, here the estimated slopes from those incubated at higher temperatures seem to be bigger on average, although the difference was not significant (_L. delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((dab_CORTHot + dab_ControlHot) - (dab_CORTCold + dab_ControlCold)),3)`, p-value = `r format_dec(pmcmc((dab_CORTHot + dab_ControlHot) - (dab_CORTCold + dab_ControlCold)),3)`; _L. guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((gab_CORTHot + gab_ControlHot)-(gab_CORTCold + gab_ControlCold)),3)`, p-value = `r format_dec(pmcmc((gab_CORTHot + gab_ControlHot)-(gab_CORTCold + gab_ControlCold)),3)`). Also, 'Control' _L. delicata_ seem to have slightly higher estimated slopes than on average ('Control' learning slope - 'CORT' learning slope = `r format_dec(mean((dab_ControlCold + dab_ControlHot) - (dab_CORTCold + dab_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((dab_ControlCold + dab_ControlHot) - (dab_CORTCold + dab_CORTHot)), 3)` ) while in _L. guichenoti_ is the opposite ('Control' learning slope - 'CORT' learning slope = `r format_dec(mean((gab_ControlCold + gab_ControlHot)-(gab_CORTCold + gab_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((gab_ControlCold + gab_ControlHot)-(gab_CORTCold + gab_CORTHot)), 3)`); nevertheless, the differences found were not significant in any case. Finally, we found that learning slopes estimated for _L. guichenoti_ assigned to group 'Blue' were marginally higher than those from _L. delicata_ (_L. delicata_ - _L. guichenoti_ = `r format_dec(mean((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((dab_CORTCold + dab_ControlCold + dab_CORTHot + dab_ControlHot) - (gab_CORTCold + gab_ControlCold + gab_CORTHot + gab_ControlHot)), 3)`).

```{r, figdeli}
#| label: figdeli
#| fig.cap: "Deli"
# First step, create the Intercepts for all models
## 1) Associative task
### Group = red
int_dar_CORTCold <- deli_red$b_Intercept
int_dar_ControlCold <- (deli_red$b_cortControl + deli_red$b_Intercept)
int_dar_CORTHot <- (deli_red$b_tempHot + deli_red$b_Intercept)
int_dar_ControlHot <- (deli_red$'b_cortControl:tempHot' + deli_red$b_cortControl + deli_red$b_tempHot + deli_red$b_Intercept)
### Group = blue
int_dab_CORTCold <- deli_blue$b_Intercept
int_dab_ControlCold <- (deli_blue$b_cortControl + deli_blue$b_Intercept)
int_dab_CORTHot <- (deli_blue$b_tempHot + deli_blue$b_Intercept)
int_dab_ControlHot <- (deli_blue$'b_cortControl:tempHot' + deli_blue$b_cortControl + deli_blue$b_tempHot + deli_blue$b_Intercept)
